A generalized definition of multidimensional item response theory parameters

### 2023-11-28 output/paper_draft/paper_M2PLM_parameters.Rmd
Omits output from the check of the parameter computation with the original ones (in the empirical example)
Renames "ITEM_SPACE" objects more properly as "TEST_SPACE"

Thus, inner product $`r LS_BASIS_INNER_PROD`$ has $`r INNER_PROD_MAT_EQ`$ as
Gram matrix, i.e. $`r INNER_PROD_EQ`$, with $`r INNER_PROD_MAT_ELEMENT_EQ`$ as
the $`r INNER_PROD_MATRIX_INDEX`$-th element of $`r INNER_PROD_MATRIX`$. As
$`r TRANSFORM_MATRIX`$ (and consequently $`r TRANSFORM_MATRIX_TRANSP`$) is
invertible, so is $`r INNER_PROD_MATRIX`$, and $`r INNER_PROD_MATRIX_INV_EQ`$.

@@

Therefore, an inner product $`r ITEM_SPACE_INNER_PROD`$ with Gram matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined, such that $`r INNER_PROD_DISCR_EQ`$
keeps the norm of $`r DISCR_VECTOR`$ invariant.
The discrimination vectors are thus represented in their own space
$`r TEST_SPACE`$ with basis $`r ITEM_SPACE_BASIS`$,
which we refer to as the *test space* [@zhang_theoretical_1999].
The test space is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.

>>>>

Thus, inner product $`r LS_BASIS_INNER_PROD`$ has $`r INNER_PROD_MAT_EQ`$ as
Gram matrix, i.e. $`r INNER_PROD_EQ`$, with $`r INNER_PROD_MAT_ELEMENT_EQ`$ as
the $`r INNER_PROD_MATRIX_INDEX`$-th element of $`r INNER_PROD_MATRIX`$. As
$`r TRANSFORM_MATRIX`$ (and consequently $`r TRANSFORM_MATRIX_TRANSP`$) is
invertible, so $`r INNER_PROD_MATRIX`$ is, and $`r INNER_PROD_MATRIX_INV_EQ`$.

@@

Therefore, an inner product $`r TEST_SPACE_INNER_PROD`$ with Gram matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined, such that $`r INNER_PROD_DISCR_EQ`$
keeps the norm of $`r DISCR_VECTOR`$ invariant.
The discrimination vectors are thus represented in their own space
$`r TEST_SPACE`$ with basis $`r TEST_SPACE_BASIS`$,
which we refer to as the *test space* [@zhang_theoretical_1999].
The test space is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.
